---
title: "Logan Graphical Analysis Report"
output: 
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
params:
  model_number: "Model 1"
  analysis_folder: NULL
  bids_dir: NULL
  blood_dir: NULL
---

For temporary debugging, this defines temporary parameters for the parameterised report

```{r}
analysis_folder <- "/home/granville/Repositories/OpenNeuro/KaSP_UCBJ_BIDS_mini/derivatives/kinfitr/Primary_Analysis/"
blood_dir <-"/home/granville/Repositories/OpenNeuro/KaSP_UCBJ_BIDS_mini/derivatives/bloodstream"
model_number <- "Model 2"
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kinfitr)
library(knitr)
library(jsonlite)
library(glue)
library(DT)
theme_set(theme_light())

theme_set(theme_light())

# Use parameters (from params or debugging section above)
analysis_folder <- params$analysis_folder %||% analysis_folder
model_number <- params$model_number %||% model_number
bids_dir <- params$bids_dir %||% bids_dir %||% NULL
blood_dir <- params$blood_dir %||% blood_dir %||% NULL

# Load configuration from standard location
config_path <- file.path(analysis_folder, "desc-kinfitroptions_config.json")
config <- NULL
if (file.exists(config_path)) {
  tryCatch({
    config <- jsonlite::fromJSON(config_path)
    # cat("Loaded config from:", config_path, "\n")
  }, error = function(e) {
    cat("Warning: Could not load config file:", e$message, "\n")
  })
} else {
  cat("Config file not found at:", config_path, "\n")
}
```

# `r params$model_number`: Logan Graphical Analysis Report

This report summarises the Logan graphical analysis results for the kinfitr analysis pipeline.

# Analysis Configuration

**Model:** `r params$model_number` - Logan (Logan Graphical Analysis)

**Analysis folder:** `r params$analysis_folder`

**Generated on:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`

# Model Configuration and Parameters

```{r model-config}
# Extract model configuration for this specific model
model_config <- NULL
if (!is.null(config$Models)) {
  if (params$model_number == "Model 1") {
    model_config <- config$Models$Model1
  } else if (params$model_number == "Model 2") {
    model_config <- config$Models$Model2
  } else if (params$model_number == "Model 3") {
    model_config <- config$Models$Model3
  }
}

if (!is.null(model_config) && model_config$type == "Logan") {
  # Create configuration table
  config_items <- list(
    "Model Type" = "Logan (Logan Graphical Analysis)"
  )

  # Add t* configuration
  config_items[["t* Value"]] <- model_config$tstar %||% "Default"
  config_items[["t* Type"]] <- if (!is.null(model_config$tstar_type)) {
    if (model_config$tstar_type == "frame") {
      "Number of Frames (from the end)"
    } else {
      "Time Point (minutes)"
    }
  } else {
    "Default"
  }

  # Handle vB parameter configuration display
  if (!is.null(model_config$vB_source)) {
    # Inheritance system (all models)
    vB_source <- model_config$vB_source

    if (vB_source == "set") {
      vB_source_display <- "Set to fixed value"
      config_items[["vB Fixed Value"]] <- model_config$vB_value %||% "Default"
    } else if (str_detect(vB_source, "inherit_model1")) {
      inherit_method <- str_split(vB_source, "_")[[1]][3]
      vB_source_display <- paste0("Inherited from Model 1 (", str_to_title(inherit_method), ")")
    } else if (str_detect(vB_source, "inherit_model2")) {
      inherit_method <- str_split(vB_source, "_")[[1]][3]
      vB_source_display <- paste0("Inherited from Model 2 (", str_to_title(inherit_method), ")")
    } else {
      vB_source_display <- vB_source
    }

    config_items[["vB Parameter Source"]] <- vB_source_display
  } else {
    # Default to set
    config_items[["vB Parameter Source"]] <- "Set to fixed value"
    config_items[["vB Fixed Value"]] <- model_config$vB_value %||% "Default"
  }

  # Add subset information if configured
  if (!is.null(model_config$subset)) {
    subset_info <- paste0(
      "Type: ", model_config$subset$type %||% "time",
      ", Start: ", model_config$subset$start %||% "Not set",
      ", End: ", model_config$subset$end %||% "Not set"
    )
    config_items[["TAC Subset"]] <- subset_info
  } else {
    config_items[["TAC Subset"]] <- "Use all frames"
  }

  config_df <- tibble(
    Parameter = names(config_items),
    Value = map_chr(config_items, as.character)
  )

  kable(config_df, caption = "Logan Model Configuration")

} else {
  cat("Logan model configuration not found or incomplete.")
}
```

```{r setup-conditions, echo=FALSE}
# Verify we have a valid Logan configuration
has_logan_config <- !is.null(model_config) && model_config$type == "Logan"

# Exit early if not a Logan configuration
if (!has_logan_config) {
  cat("Invalid or missing Logan configuration. This report should not have been generated.")
  knitr::knit_exit()
}
```

# Loading Data

## Loading TAC Data

```{r load-tacs}
weights_files <- list.files(analysis_folder,
                        pattern = "*_weights.tsv",
                        recursive = TRUE)

weightsdata <- tibble(
  filename = weights_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr:::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>% 
  unnest(tacs) %>% 
  select(-filename, -basename, -measurement, -desc, -TAC)
  

tacs_files <- list.files(analysis_folder,
                        pattern = "*_desc-combinedregions_tacs.tsv",
                        recursive = TRUE)

tac_data <- tibble(
  filename = tacs_files) %>%
  mutate(basename = basename(filename)) %>%
  mutate(attributes = map(filename, kinfitr:::bids_filename_attributes)) %>%
  unnest(attributes) %>%
  group_by(filename) %>%
  mutate(tacs = map(filename, ~read_tsv(file.path(analysis_folder, .x), show_col_types = FALSE))) %>%
  ungroup() %>% 
  unnest(tacs) %>% 
  select(-basename, -measurement, -desc) %>% 
  inner_join(weightsdata)
```

Because we are now working with kinetic modelling, we need to use minutes instead of seconds. Hence, we will henceforth use minutes for time.

```{r}
tac_data <- tac_data %>% 
  mutate(frame_start = frame_start/60,
         frame_end = frame_end/60,
         frame_dur = frame_dur/60,
         frame_mid = frame_mid/60)
```


## Loading Blood Data

```{r blood-loading-setup, echo=FALSE}
# Determine which blood loading approach to use
if (!is.null(blood_dir)) {
  use_blood_dir <- TRUE
  use_analysis_folder <- FALSE
  use_bids_raw <- FALSE
} else {
  use_blood_dir <- FALSE
  blood_source <- determine_blood_source(analysis_folder, bids_dir)
  use_analysis_folder <- blood_source == "analysis_folder"
  use_bids_raw <- blood_source == "bids_dir"
}
```

```{r load-from-blood-dir, eval=use_blood_dir, echo=use_blood_dir}
# Load blood data from specified blood_dir
inputfunction_files <- list.files(blood_dir, pattern = "*_inputfunction\\.tsv$", recursive = TRUE, full.names = TRUE)

if (length(inputfunction_files) == 0) {
  stop("No inputfunction.tsv files found in blood_dir: ", blood_dir)
}

blood_data <- kinfitr::bloodstream_import_inputfunctions(blood_dir) %>% 
  select(-measurement)
```

```{r load-from-analysis-folder, eval=use_analysis_folder, echo=use_analysis_folder}
# Load processed inputfunction files from analysis folder
inputfunction_files <- list.files(analysis_folder, pattern = "*_inputfunction\\.tsv$", recursive = TRUE, full.names = TRUE)

if (length(inputfunction_files) == 0) {
  stop("No inputfunction.tsv files found in analysis_folder: ", analysis_folder)
}

blood_data <- kinfitr::bloodstream_import_inputfunctions(analysis_folder) %>% 
  select(-measurement, -desc)
```

```{r create-analysis-inputfunctions, eval=use_bids_raw, echo=use_bids_raw, results='asis'}
str_glue("Because we are loading blood data from the raw BIDS folder, we will first generate 
         an arterial input function using linear interpolation of the measured curves,
         and then create *_inputfunction.tsv files in the kinfitr analysis folder.")
```

```{r load-from-bids-raw, eval=use_bids_raw}
# Load blood files from bids_dir
blood_files <- list.files(bids_dir, pattern = "*_blood\\.tsv$", recursive = TRUE, full.names = TRUE)

if (length(blood_files) == 0) {
  stop("No _blood.tsv files found in bids_dir")
}

# Generate blood data from raw BIDS data
raw_data <- kinfitr::bids_parse_study(bids_dir) %>% 
  select(any_of(names(tac_data)), blooddata)

tac_data_files <- tac_data %>% 
  filter(!duplicated(filename)) %>% 
   select(any_of(names(raw_data)), filename)

save_data <- inner_join(raw_data, tac_data_files) %>% 
  mutate(filename = str_remove(filename, "_desc.*")) %>% 
  mutate(filename = str_remove(filename, "_weights.*")) %>% 
  mutate(filename = str_remove(filename, "_tacs.*")) %>% 
  mutate(filename = paste0(filename, "_inputfunction.tsv")) %>% 
  mutate(filename = paste0(analysis_folder, "/", filename))

walk2(save_data$blooddata, save_data$filename, blooddata2inputfunction_tsv)

# Load the created inputfunction files
blood_data <- kinfitr::bloodstream_import_inputfunctions(analysis_folder) %>% 
  select(-measurement, -desc)
```

```{r blood-loading-error, eval=(!use_blood_dir && !use_analysis_folder && !use_bids_raw)}
stop("No blood data available - provide blood_dir or ensure blood data exists in analysis folder or BIDS directory")
```

## Loading Delay Information

```{r load-delay}
delay_data <- tibble(
  filename = list.files(analysis_folder, pattern = "*_desc-delayfit_kinpar.tsv", 
                       recursive = TRUE, full.names = TRUE)
)

if( nrow(delay_data)==0 ) {
  cat("No delay data found for kinetic modelling.")
  cat("Delay will be set to 0.")
  
  delay_source <- "Not estimated: assumed to be zero"
  
  delay_data <- blood_data %>% 
    select(-input) %>% 
    mutate(inpshift = 0)
  
} else{
  
  delay_data <- delay_data %>% 
    mutate(attributes = map(filename, kinfitr:::bids_filename_attributes)) %>%
    unnest(attributes) %>% 
    filter(!is.na(sub)) %>% 
    mutate(pet = str_remove(basename(filename), "_model.*.*")) %>%
    mutate(pet = str_remove(basename(pet), "_desc.*")) %>%
    mutate(pet = str_remove(pet, "_kinpar.*")) %>% 
    mutate(
      inpshift = map_dbl(filename, ~{
          tryCatch({
            delay <- read_tsv(.x)
            if (!is.null(delay$blood_timeshift)) {
              delay$blood_timeshift
            } else {
              0  # Default to zero if no delay found
            }
          }, error = function(e) 0)  # Default to zero on error
        })
      ) %>% 
    select(-filename, -measurement, -model, -desc)
  
  delay_source <- "Inherited from delay fit"
}
```


```{r vB-loading-setup, echo=FALSE}
# Determine inheritance for vB
if(!is.null(model_config$vB_source) && 
   str_detect(model_config$vB_source, "inherit")) {
  vB_inheritance <- TRUE
} else {
  vB_inheritance <- FALSE
}
```


```{r heading-vB, echo=vB_inheritance, eval=vB_inheritance, results='asis'}
str_glue("## Loading vB Information
         
         The model has been defined to inherit a vB value from a previous model run.
         ")
```


```{r load-vB, echo=vB_inheritance, eval=vB_inheritance}
vB_inheritance_model <- str_match(model_config$vB_source, "inherit_(model\\d)")[,2]
vB_inheritance_type <- str_match(model_config$vB_source, "inherit_model\\d_(\\w*)")[,2]

vB_data <- tibble(
  filename = list.files(analysis_folder, 
                        pattern = paste0("*_desc-", vB_inheritance_model,"_kinpar.tsv"), 
                       recursive = TRUE, full.names = TRUE)
)

if( nrow(vB_data)==0 ) {
  cat("No vB data found for inheritance.")
  cat("vB will be set to 0.05")
  
  vB_data <- blood_data %>% 
    select(-input) %>% 
    mutate(vB = 0.05)
  
} else{
  
  vB_data <- vB_data %>% 
    mutate(attributes = map(filename, kinfitr:::bids_filename_attributes)) %>%
    unnest(attributes) %>% 
    filter(!is.na(sub)) %>% 
    mutate(pet = str_remove(basename(filename), "_model.*.*")) %>%
    mutate(pet = str_remove(basename(pet), "_desc.*")) %>%
    mutate(pet = str_remove(pet, "_kinpar.*")) %>% 
    mutate(vB_kp = map(filename, read_tsv)) %>% 
    select(-filename, -measurement, -desc) %>% 
    group_by(pet)
  
  # Calculation
  if(vB_inheritance_type == "mean") {
    vB_data <- vB_data %>% 
      mutate(vB=map_dbl(vB_kp, ~mean(.x$vB))) %>% 
    select(-vB_kp) %>% 
    ungroup()
  }
  
  if(vB_inheritance_type == "median") {
  vB_data <- vB_data %>% 
    mutate(vB=map_dbl(vB_kp, ~median(.x$vB))) %>% 
    select(-vB_kp) %>% 
    ungroup()
  }
  
  if(vB_inheritance_type == "regional") {
  vB_data <- vB_data %>% 
    mutate(vB_kp = map(vB_kp, ~.x %>% 
                         select(region, vB))) %>% 
    unnest(vB_kp) %>% 
    ungroup()
  }
}
```




# Combining Data

```{r}
tac_data_nested <- tac_data %>% 
  group_by(across(intersect(colnames(.), c("sub", "ses", "trc", "rec", "task", 
                                           "run", "pet", "filename", "region")))) %>% 
  nest(.key="tacs")

model_data <- inner_join(tac_data_nested, blood_data) %>% 
  ungroup() %>% 
  mutate(output_stem = filename) %>% 
  select(-filename) %>% 
  mutate(output_stem = str_remove(output_stem, "_desc.*")) %>% 
  mutate(output_stem = str_remove(output_stem, "_weights.*")) %>% 
  mutate(output_stem = str_remove(output_stem, "_tacs.*"))

model_data <- model_data %>% 
  left_join(delay_data)
```

```{r combine-vB, echo=vB_inheritance, eval=vB_inheritance}
model_data <- model_data %>% 
  left_join(vB_data)
```


# Logan Model Fitting

Now we proceed to the actual 2TCM model fitting using all available regional TACs.


```{r model-prep}
# Set vB if not being fit or inherited
if(vB_source=="set") {
  model_data$vB <- model_config$vB$start %||% 0.05
}

# Extract TAC subset parameters
subset_config <- model_config$subset
frameStartEnd <- NULL
timeStartEnd <- NULL

if (!is.null(subset_config) && (!is.null(subset_config$start) || !is.null(subset_config$end))) {
  if (subset_config$type == "frame") {
    frameStartEnd <- c(subset_config$start, subset_config$end)
  } else if (subset_config$type == "time") {
    timeStartEnd <- c(subset_config$start, subset_config$end)
  }
}
```

```{r model-fitting}
# Safe Logan function to handle errors
safe_Loganplot <- possibly(Loganplot, otherwise = NA)

if(config_items$`t* Type` == "Number of Frames (from the end)") {

  model_data <- model_data %>% 
    group_by(output_stem, region) %>% 
    mutate(fit_Logan = pmap(list(tacs, input, inpshift, vB),
                           ~Loganplot(
                             t_tac = ..1$frame_mid, 
                             tac = ..1$TAC, 
                             input = ..2, 
                             tstarIncludedFrames = 
                               as.numeric(config_items$`t* Value`),
                             inpshift = ..3,
                             vB = ..4,
                             dur = ..1$frame_dur,
                             frameStartEnd = frameStartEnd,
                             timeStartEnd = timeStartEnd))) %>%
    ungroup() %>% 
    mutate(success = map_dbl(fit_Logan, length) > 1)
  
} else {
  
    model_data <- model_data %>% 
    group_by(output_stem, region) %>% 
    mutate(fit_Logan = pmap(list(tacs, input, inpshift, vB),
                           ~Loganplot(
                             t_tac = ..1$frame_mid, 
                             tac = ..1$TAC, 
                             input = ..2, 
                             tstar = 
                               as.numeric(config_items$`t* Value`),
                             inpshift = ..3,
                             vB = ..4,
                             dur = ..1$frame_dur,
                             frameStartEnd = frameStartEnd,
                             timeStartEnd = timeStartEnd))) %>%
    ungroup() %>% 
    mutate(success = map_dbl(fit_Logan, length) > 1)
  
}


```

```{r, results='asis'}
success_n <- sum(model_data$success)
tot_n <- nrow(model_data)

str_glue("Model successfully estimated for {success_n} / {tot_n} ({round(100*success_n/tot_n)}%) of measurements.
         
         Model estimation unsuccessful for {tot_n-success_n} / {tot_n}  ({100-(round(100*success_n/tot_n))}%) of measurements.")
```


## VT Estimates

```{r vt-estimates}
cat("Volume of distribution (VT) estimates will show:")
cat("\n- VT values for each TAC")
cat("\n- Uncertainty estimates")
cat("\n- Goodness of linear fit (R²)")
cat("\n- Intercept values")
```

## Logan Plots Visualisation

```{r logan-plots, fig.height=8, fig.width=12}
cat("Logan plot visualisation will include:")
cat("\n- Logan plots for each TAC showing linear fit")
cat("\n- t* selection and linear range")
cat("\n- Residuals from linear fit")
cat("\n- VT distribution across regions")
```

## t* Selection Analysis

```{r tstar-analysis}
cat("t* (start time) analysis will show:")
cat("\n- Optimal t* selection for each TAC")
cat("\n- Sensitivity analysis of VT to t* choice")
cat("\n- Linearity metrics vs. t* value")
cat("\n- Recommended t* based on data quality")
```

## Regional VT Summary

```{r regional-vt}
cat("Regional VT summary will display:")
cat("\n- Mean VT values by region")
cat("\n- VT variability across subjects")
cat("\n- Expected regional patterns")
cat("\n- Comparison with literature values")
```

## Quality Control

```{r logan-qc}
cat("Logan analysis quality control:")
cat("\n- Linearity assessment (R² > 0.95 recommended)")
cat("\n- Appropriate t* selection")
cat("\n- VT values within physiological range")
cat("\n- Consistent results across similar regions")
cat("\n- Blood volume correction validation")
```

## Advantages and Limitations

```{r logan-notes}
cat("Logan graphical analysis:")
cat("\n")
cat("**Advantages:**")
cat("\n- Model-independent approach")
cat("\n- Robust to noise in late time points")
cat("\n- Does not require specific compartmental assumptions")
cat("\n")
cat("**Limitations:**")
cat("\n- Requires identification of linear phase")
cat("\n- Less precise than full kinetic modeling")
cat("\n- Cannot separate specific and non-specific binding")
```

## Next Steps

After reviewing this report:

1. **Verify linearity**: Ensure good linear fits in Logan plots (R² > 0.95)
2. **Check t* selection**: Confirm appropriate start time for linear phase
3. **Assess VT values**: Verify physiologically reasonable distribution volumes
4. **Compare with compartmental models**: Evaluate consistency with 1TCM/2TCM results

## Session Information

```{r session-info}
sessionInfo()
```